---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

```


`gbtransparency` is primarily a data package enabling an efficient method for working with [Green Bond Transparency datasets](https://www.greenbondtransparency.com/support/resources/) in R. 

### About the Green Bond Transparency datasets:

The Green Bond Transparency(GBTP) has developed a free and public integrated dataset of all the bond's information included in the platform presented in five export-files.  `gbtransparency` helps users to access files. These files are: 

(1) `bond's` general information 
(2) `allocation` of proceeds to project categories using international standards (GBP, CBI) 
(3) `measurements` of impact and outcome KPIs
(4) individual bond-`tranche` information 
(5) detailed information of the `projects` receiving disbursements.

There is also an additional file named `index`. This shows description of variable names per data.

### Relevant Notes

1. **`gbtransparency` is still under heavy development**: Please use accordingly. The initial phase of package development aims to finalize stable versions of the datasets, and will be announced with a new package version release and note. Further development will focus on building helper functions to aid efficient analysis workflows with the dataset.

2. **`gbtransparency` is a personal project**:  While the package author works as a [consultant to AidData](https://www.linkedin.com/feed/update/urn:li:activity:7067478837885849600/) this package is a personal project. The author built the package for his own own use, but hopes that it can grow into a robust package that can aid researchers, policymakers, and others interested in gaining actionable, empirically-based insights about Green Bond Transparency datasets. 

## Installation

You can install the development version of `gbtransparency` from [GitHub](https://github.com/) with:

``` r
# install the `devtools` package if not yet installed
# install.packages("devtools")

# install chinadevfin2 from GitHub
devtools::install_github("Teal-Insights/gbtransparency")
```

This package will likely never be published on [CRAN](https://cran.r-project.org/) because the data file sizes are too big.

## Using gbtransparency package

The datasets in the packages are as follow:
```{r echo=FALSE, message=FALSE,warning=FALSE}
library(dplyr)
library(gbtransparency)

base::data.frame(
  package_data_name = c(
    "gbt_allocations",
  "gbt_bonds",
  "gbt_key_performance_indicators",
  "gbt_projects",
  "gbt_tranches",
  "gbt_data_dictionary"),
website_data_description = c(
  "allocation of proceeds to project categories using international standards (GBP, CBI)",
  "bond's general information",
  "measurements of impact and outcome KPIs",
  "detailed information of the projects receiving disbursements",
  "individual bond-tranche information",
  "index (description of variable names per data.)")
) %>% knitr::kable()
```

```{r}

```

Now we can have a look at the first six observations per data

```{r example}

```

```{r}

```
a) `gbt_allocations`:	allocation of proceeds to project categories using international standards (GBP, CBI)
```{r}
utils::head(x = gbt_allocations) %>% knitr::kable()
```

```{r}

```
b) `gbt_bonds`:	bond’s general information
```{r}
utils::head(x = gbt_bonds) %>% knitr::kable()
```

```{r}

```
c) `gbt_key_performance_indicators`:	measurements of impact and outcome KPIs
```{r}
utils::head(x = gbt_key_performance_indicators) %>% knitr::kable()
```

```{r}

```
d) `gbt_projects`:	detailed information of the projects receiving disbursements
```{r}
utils::head(x = gbt_projects) %>% knitr::kable()
```

```{r}

```
e) `gbt_tranches`:	individual bond-tranche information
```{r}
utils::head(x = gbt_tranches) %>% knitr::kable()
```

```{r}

```
f) `gbt_data_dictionary`:	index (description of variable names per data.)
```{r}
utils::head(x = gbt_data_dictionary) %>% knitr::kable()
```

```{r}

```
